---
title: '**Título bué fixe**'
author:
  - name: 'André Silvestre'
    affil: 20240502
    main: true
  - name: 'Umeima Mahomed'
    affil: 20240543
    main: true
title_textsize: '100pt'
font_family: "Rasa"
titletext_fontfamily: "Rasa"
poster_height: 48in
poster_width: 36in


logoleft_name: './Logo-Nova-IMS-White.png'

primary_colour:	  "#008080"	 # Main colour used for poster design.
secondary_colour:	"#0b4545"	 # Secondary colour use for poster design.
accent_colour:	  "#cc0000"	 # A third colour option for adding some "pop" to the poster colour palette.

output: 
  posterdown::posterdown_html:
    self_contained: TRUE
    pandoc_args: --mathjax
    number_sections: TRUE
    css: "SfDS_Poster_20240502.css"
bibliography: packages.bib
csl: apa.csl
link-citations: true
columnline_col: "#fff"
columnline_width: 0mm

---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%",
                      format = "html")
options(knitr.table.format = "html") 

# pagedown::chrome_print("myfile.Rmd") # to print the poster to pdf
# install.packages("citr")             # to insert citations
# https://github.com/brentthorne/posterdown/wiki/posterdown_html # to see more options
```

# Introduction

This is the `posterdown_betterport` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

## Objectives

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki) and the [@Teste] and [@

**_Now on to the results!_**

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='<span class="caption-text">Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).</span>', fig.height=6, out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='<span class="caption-text">Boxplots, so hot right now!</span>', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal Length",
                             "Sepal Width",
                             "Petal Length",
                             "Petal Width",
                             "Species"),
  escape = TRUE)
```

# References
